tstrait: a quantitative trait simulator for ancestral recombination graphs

### 2024-03-12 paper.tex
Daiki's changes

\begin{figure*}[t]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=213pt]{figures/time-scaling.pdf}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point
represents the mean time for 10 independent runs under different random seeds.
The times reported are the total CPU time required to simulate quantitative
traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM. The trait model
is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and
$\alpha=-1$. (A) CPU time with increasing number of individuals
based on ARGs simulated using \texttt{stdpopsim} with the HomSap
demographic mode. For each replicate we simulate
one quantitative trait with 1000 causal sites.
(B) CPU time with increasing number of causal sites on two large ARGs.
\texttt{tstrait} is used to simulate quantitative traits from
the simulated French Canadian dataset \citep{anderson2023} and the inferred
tree sequence dataset of the 1000 Genomes Project \citep{kelleher2019} with
varying number of causal sites. The French Canadian dataset is downloaded from
\url{https://zenodo.org/record/6839683}, and the inferred ARG from the 1000
Genomes Project is downloaded from \url{https://zenodo.org/record/3051855}.
Chromosome 9 is selected for both datasets.}\label{fig:time}
\end{figure*}

\begin{figure*}[t]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=213pt]{figures/time-scaling.pdf}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point
represents the mean time for 10 independent runs under different random seeds with 95\% confidence intervals plotted.
The times reported are the total CPU time required to simulate quantitative
traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM. The trait model
is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and
$\alpha=0$. \texttt{tstrait} is used to simulate quantitative traits from ARGs simulated using \texttt{stdpopsim} with the generic piecewise constant size model in Homo Sapiens catalog. For each replicate we simulate one quantitative trait with 1000 causal sites. We have compared \texttt{tstrait} against the quantitative trait simulation framework that is based on \texttt{tskit} functionalities. The comparison codes are adapted from \citep{martin2017}, and they are modified based on functionalities offered in \texttt{tskit} version 0.5.6 to speed up the computational efficiency.}\label{fig:time}
\end{figure*}
\end{document}

>>>>

\begin{figure*}[t]%
\centering
% FIXME get the sizes right here and in the notebook where we're generating
% the figure so we don't have to scale here.
\includegraphics[width=\columnwidth]{figures/computational-time-code/stdpopsim-time.pdf}
\caption{\textbf{Time taken to simulate quantitative traits.} Each point
represents the mean time for 10 independent runs under different random seeds with 95\% confidence intervals plotted.
The times reported are the total CPU time required to simulate quantitative
traits on an Intel(R) Core(TM) i9-11900H CPU and 16 GB of RAM. The trait model
is a normal distribution with $\mu=0$, $\sigma^2=1$, $h^2=0.3$, and
$\alpha=0$. \texttt{tstrait} is used to simulate quantitative traits from ARGs simulated using \texttt{stdpopsim} with the generic piecewise constant size model in Homo Sapiens catalog. For each replicate we simulate one quantitative trait with 1000 causal sites. We have compared \texttt{tstrait} against the quantitative trait simulation framework that is based on \texttt{tskit} functionalities. The comparison codes are adapted from \citep{martin2017}, and they are modified based on functionalities offered in \texttt{tskit} version 0.5.6 to speed up the computational efficiency.}\label{fig:time}
\end{figure*}
\end{document}
